---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(reohelpers)
library(ggplot2)
library(dplyr)
```

# reohelpers

<!-- badges: start -->
<!-- badges: end -->

The goal of reohelpers is to make te reo easier to use in R.

## Installation

reohelpers is not yet released on [CRAN](https://CRAN.R-project.org) but you can install the development version from [GitHub](https://github.com/) with:

```r
# install.packages("devtools")
devtools::install_github("joevalalipin/reohelpers")
```

## Overview

* `add_macron()` adds macrons appropriately to vowels in te reo words or phrases.
* `macron_vowel()` adds macrons to single or multiple vowels in a given string.
* `meaning()` returns a dataframe of meanings of each word in a given string.

## Examples

### add_macron()

```{r}
ggplot(mtcars, aes(x = cyl, y = hp, group = cyl)) +
  geom_boxplot() +
  labs(title = add_macron("Number of cylinders and horsepower in motoka dataset")) +
  theme_classic()
```

### macron_vowels()

```{r}
# data.frame(vowel = c("a", "e", "i", "o", "u")) %>% 
#   mutate(macrons = macron_vowel(vowel))
```

### meaning()
```{r}
```



