---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE,
                      comment = "#>",
                      fig.path = "man/figures/README-",
                      out.width = "100%")

library(reohelpers)
library(ggplot2)
library(dplyr)
library(readr)
```

# reohelpers

<!-- badges: start -->
<!-- badges: end -->

The goal of reohelpers is to make te reo easier to use in R.

## Installation

reohelpers is not yet released on [CRAN](https://CRAN.R-project.org) but you can install the development version from [GitHub](https://github.com/) with:

```r
# install.packages("devtools")
devtools::install_github("joevalalipin/reohelpers")
```

## Overview

* `add_macron()` adds macrons appropriately to vowels in te reo words or phrases.
* `macron_vowel()` adds macrons to single or multiple vowels in a given string.
* `meaning()` returns a dataframe of meanings of each word in a given string.

## Examples

### add_macron()

Usually the data comes without macron accents
```{r fig.height=10}
infringements <- read_csv("data/infringements.csv")
infringements %>% 
  ggplot(aes(x = `Infringement notices`, y = reorder(Council, -`Infringement notices`))) +
  geom_col() +
  labs(title = "Number of infringement notices issued by councils\nin 2018-19",
       x = "",
       y = "",
       caption = "Putake: Manatu Mo Te Taiao") +
  scale_x_continuous(expand = c(0, 0)) +
  theme_classic()
```

Using the function would add appropriate macrons to place names and words
```{r fig.height=10}
infringements %>% 
  mutate(Council = add_macron(Council)) %>% 
  ggplot(aes(x = `Infringement notices`, y = reorder(Council, -`Infringement notices`))) +
  geom_col() +
  labs(title = "Number of infringement notices issued by councils\nin 2018-19",
       x = "",
       y = "",
       caption = paste0(add_macron("Putake"), ": Ministry for the Environment")) +
  scale_x_continuous(expand = c(0, 0)) +
  theme_classic()
```


### macron_vowel()
If for any reason you need to add macron to a specific character in a string use `macron_vowel()`: `r macron_vowel("a e i o u")`

### meaning()
A quick way to get the meaning of te reo words. 
```{r}
meaning("reo")
```

Not advised for phrases but it gives you the idea.
```{r}
meaning("kia ora")
```



